Which ``Bad Smells'' Can Be Ignored?

### 2016-03-13 Manuscript.tex
Updates from ShareLaTeX

To address this problem, we propose the XTREE
tool to judge refactorings
proposed by developers.
  XTREE requires:
     \begin{itemize}
         \item A historical log of defects seen previously in the code;
         \item  Bad smells expressed in terms of the 
          metrics   in that log;
         \item Some proposed refactorings justified using those bad smells.
     \end{itemize}
Given that information,  XTREE can determine which
  proposed refactorings are to be ignored
since they are not justifiable  
with respect to the history of the project.

XTREE addresses four problems that  make it hard to  learn useful
bad smells for a particular project.

@@

{\em PROBLEM \#2:} Not all bad smells can be fixed. 
Consider
a bad smell stemming from a long method,
yet that method must be passed as a single closure
to a third-party GUI toolkit.  This is one
example of a common problem-- when new code must
be combined with code from other developers,
sometimes the constraints imposed by the other code
lead unavoidably to bad smells. In this case,
a refactoring proposed to reduce that bad smell
may be irrelevant since it cannot be applied to this code base.

@@

\newpage
\subsubsection{ Alves et al.}
Alves et al.~\cite{Alves2010} propose another approach
to finding thresholds that  utilizes the underlying statistical distribution and scale of the metrics. 
Metric values for each class are weighted according to the source lines of code (SLOC) of the class. All the weighted metrics are then normalized by the sum of all weights of for the system. 
The normalized metric values are ordered in an ascending fashion (this is equivalent to computing a density function, in which the x-axis represents the weight ratio (0-100\%), and the y-axis the metric scale).
Alves et al. then select a percentage value (they suggest 90\%) which represents the ``normal'' values for metrics. The metric threshold, then, is the metric value for which 90\% of the classes fall below. The intuition  is that the worst code has outliers beyond 90\% of the normal code measurements. Hermans et al.~\cite{hermans15} used the
Alves et al. method in their  2015 paper on
exploring bad smells.

@@

\input{tex/prediction_stats.tex}

\section{Evaluation}
\subsection{Research Questions}
% To define our experiments, we  review some details
% about XTREE.

@@

\input{tex/rq2.tex}

\subsection{Results}

>>>>

To address this problem, we propose the XTREE
tool that uses: 
     \begin{itemize}
         \item A historical log of defects seen previously in the code;
         \item  Bad smells expressed in terms of the 
          metrics   in that log;
         \item Some proposed refactorings justified using those bad smells.
     \end{itemize}
Given that,  XTREE can determine which
  proposed refactorings are to be ignored
since they are not justifiable  
with respect to the history of the project. XTREE addresses four problems that  make it hard to  learn useful
bad smells for a particular project.

@@

{\em PROBLEM \#2:} Not all bad smells can be fixed. 
When new code must
be combined with code from a third party, 
sometimes the constraints of that code 
lead unavoidably to bad smells violations (e.g.
developers might need to passed as a single closure a  very long method
to  a third-party GUI toolkit).   In this case,
a refactoring proposed to reduce that bad smell
may be irrelevant since it cannot be applied to this code base.

@@

\subsubsection{ Alves et al.}
Alves et al.~\cite{Alves2010} propose another approach
to finding thresholds that  utilizes the underlying statistical distribution and scale of the metrics. 
Metric values for each class are weighted according to the source lines of code (SLOC) of the class. All the weighted metrics are then normalized by the sum of all weights of for the system. 
The normalized metric values are ordered in an ascending fashion (this is equivalent to computing a density function, in which the x-axis represents the weight ratio (0-100\%), and the y-axis the metric scale).
Alves et al. then select a percentage value (they suggest 90\%) which represents the ``normal'' values for metrics. The metric threshold, then, is the metric value for which 90\% of the classes fall below. The intuition  is that the worst code has outliers beyond 90\% of the normal code measurements. Hermans et al.~\cite{hermans15} used the
Alves et al. method in their  2015 paper on
exploring bad smells.

@@

\input{tex/prediction_stats.tex}      
	\newpage     
\section{Evaluation}
\subsection{Research Questions}
% To define our experiments, we  review some details
% about XTREE.

@@

\input{tex/rq2.tex}
 \newpage
\subsection{Results}
